---
title: "p8105_hw1_zl2746"
author: "Ze Li"
date: "2023-09-15"
output: github_document
---


```{r library, message = FALSE}
#install.packages("moderndive")
library(moderndive)
library(tidyverse)
```


# Problem 1

```{r data description}
data("early_january_weather")
summary(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
```

There are 15 variables in `early_january_weather` dataset.

There are 4 time variables: year, month, day and hour. 

The year variable is 2013 and all data is happened in this year. 

The month variable is 1 which means all data is happened in Jan 2013.

The day variable has min value 1 and max value 15, which means that
the dataset only has 15 days in 2013.

The hour variable has min value 0 and max value 23, which means that 
it measures 23 hours in a day.

The other 11 variables are factors of weather.

The temperature variable ranged from 24.08 to 57.92, having a mean of 39.58.

The dewp variable ranged from 8.96 to 53.06.

The humid variable ranged from 32.86 to 100.

The wind_direction variable ranged from 0 to 360, having 5 null values.

The wind_speed variable ranged from 0 to 24.166.

The wind_gust variable ranged from 16.11 to 31.07, having 308 null values.

The precip variable ranged from 0 to 0.19.

The pressure variable ranged from 1011 to 1034, having 38 null values.

The visible variable ranged from 0.12 to 10.

The time_hour variable ranged from 2013-01-01 01:00:00.00 to 2013-01-15 23:00:00.00.

The dataset has 358 rows and 15 columns.

Next, making a scatterplot of `temp (y)` vs `time_hour (x)`.

```{r scatterplot}
ggplot(early_january_weather, 
       aes(x=temp, y=time_hour, color = humid,
           xlab = 'temperature'), ylab = 'time hour') + geom_point()
ggsave('temp_vs_timehour_by_humid.pdf')
```

In the first 10 days, there is low temperature below around 50, and humid is below
around 60. 

During day 10 to day 14, the temperature gradually increase to the maximum 
around 60 and humid increases to 100 as color becomes lighter. 

In the last day,
the temperature decreases suddenly to 40.

# Problem 2

```{r df}
problem2_df=
  tibble(
    samp=rnorm(10,sd = 1),
    vec_logical = samp>0,
    vec_char = c('book','mac','bag','ipad','phone','coffee','hat','water','mouse','pen'),
    vec_factor = c('low','medium','high','low','medium','high','low','medium','high','low')
)    
problem2_df
```

Using `as.numeric` function,

```{r mean}
as.numeric(problem2_df$samp)
as.numeric(problem2_df$vec_logical)
as.numeric(problem2_df$vec_char)
as.numeric(problem2_df$vec_factor)
mean(problem2_df$samp)
mean(problem2_df$vec_logical)
mean(problem2_df$vec_char)
mean(problem2_df$vec_factor)
```

Using `pull` function,

```{r pull}
mean(problem2_df %>% pull(samp))
mean(problem2_df %>% pull(vec_logical))
mean(problem2_df %>% pull(vec_char))
mean(problem2_df %>% pull(vec_factor))
```

The normal distribution and logical vector have mean of 0.0496 and 0.5,
since the logical vector is transfer into 0 and 1.

However, character vector and factor vector don't work to take mean.
Both of them are transferred into NA.
